### 2019-02-28 UnderstandabilityPaper/machinelearning.tex
Add default.nix to understandability

I meant to send this earlier, in case it's useful. These are just some
things that came to mind regarding "explainable" AI and machine
learning. Lots of rambling, but hopefully some insight into current
machine-learning thinking (as I understand it, as somewhat of an
outsider!).

@@

Another example is learning to recognise and generate hand-written
characters by using a differentiable program for drawing lines:
https://web.mit.edu/cocosci/Papers/Science-2015-Lake-1332-8.pdf‎

@@

https://en.wikipedia.org/wiki/Adversarial_machine_learning

@@

A similar effect to the structured "latent space" of the VAE has been
found with word2vec:
https://en.wikipedia.org/wiki/Word2vec#Preservation_of_semantic_and_syntactic_relationships

@@

>>>>

% STRUCTURE:

%  - Understandability in AI
%  - Theorem proving as example:
%   - Least informative

\documentclass{article}
\begin{document}
I meant to send this earlier, in case it's useful. These are just some
things that came to mind regarding "explainable" AI and machine
learning. Lots of rambling, but hopefully some insight into current
machine-learning thinking (as I understand it, as somewhat of an
outsider!).

@@

Another example is learning to recognise and generate hand-written
characters by using a differentiable program for drawing lines:
https://web.mit.edu/cocosci/Papers/Science-2015-Lake-1332-8.pdf

@@

% https://en.wikipedia.org/wiki/Adversarial_machine_learning

@@

A similar effect to the structured "latent space" of the VAE has been
found with word2vec:

% https://en.wikipedia.org/wiki/Word2vec#Preservation_of_semantic_and_syntactic_relationships

@@

\bibliographystyle{plain}
\bibliography{./Bibtex}

\end{document}
